Compositional equivalences based on Open pNets

### 2021-08-20 2016-Weak-FH-Bisim/WeakBisim.tex
Two easy comments
Meeting

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely. This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not).

@@

This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition. Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters. Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes. We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional. Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.

>>>>

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely. This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not). Compared to the definition of open transition, this small change has the significant impact as a single weak transition is the composition of several transitions of the holes.

@@

This article defines a strong and a weak bisimulation relation that are adapted to parameterised systems and hierarchical composition. Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters. Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes. We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional. Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
